### 2020-03-18 2020.csic5011/homework/homework05.tex
Add files via upload

\lecture{Homework 4. SDP Extensions of PCA/MDS}{Yuan Yao}{Due: Open Date}{Mar 15, 2019}

@@

When $\theta=\infty$ without noise, classical MDS will work; but for a finite $\theta$ with noisy measurements, SDP approach can be useful. You may try the matlab package SNLSDP by Kim-Chuan Toh, Pratik Biswas, and Yinyu Ye, downladable at \url{http://www.math.nus.edu.sg/~mattohkc/SNLSDP.html}.

>>>>

\lecture{Homework 5. SDP Extensions of PCA and MDS}{Yuan Yao}{Due: 1.5 weeks}{Mar. 18, 2020}

@@

When $\theta=\infty$ without noise, classical MDS will work; but for a finite $\theta$ with noisy measurements, SDP approach can be useful. You may try the matlab package SNLSDP by Kim-Chuan Toh, Pratik Biswas, and Yinyu Ye, or the facial reduction speed up by Nathan Krislock and Henry Wolkowicz.
